Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-04-19 WSSSPE2_report/WSSSPE2_review.tex
Section 10: Add top #WSSSPE tweets (to be continued)

\author{Daniel S. Katz$^{(1)}$, Sou-Cheng T. Choi$^{(2)}$, Nancy Wilkins-Diehr$^{(3)}$, Neil Chue Hong$^{(4)}$, 
\\ James Howison$^{(5)}$, Miguel de Val-Borro$^{(6)}$, Richard Littauer$^{(7)}$ 
\\ more TBD by contributions 
\\ 
{\scriptsize\today \quad  (Due:  $\backsim$ April 30)}} 
%\author{Gabrielle Allen$^{(11)}$,  \\
%Karen Cranston$^{(4)}$, Manish Parashar$^{(5)}$, David Proctor$^{(6)}$, \\
%Matthew Turk$^{(2)}$, Colin C. Venters$^{(7)}$,  Miguel de Val-Borro$^{(10)}$}
%
\thanks{{}$^{(1)}$ Computation Institute, University of Chicago \& Argonne National Laboratory, Chicago, IL, USA}
%
\thanks{{}$^{(2)}$ NORC at the University of Chicago and   Illinois Institute of Technology, Chicago, IL, USA}
%
\thanks{{}$^{(3)}$ University of California-San Diego, San Diego, CA, USA}
%
\thanks{{}$^{(4)}$ Software Sustainability Institute, University of Edinburgh, Edinburgh, UK}
%
\thanks{{}$^{(5)}$ TBD}
%
\thanks{{}$^{(6)}$ TBD}  
%
\thanks{{}$^{(7)}$ TBD}   
%  
%\thanks{{}$^{(4)}$ National Evolutionary Synthesis Center, Durham, NC, USA}
%
%\thanks{{}$^{(5)}$ Rutgers Discovery Informatics Institute, Rutgers University, New Brunswick, NJ, USA}
%
%\thanks{{}$^{(6)}$ International Consortium of Research Staff Associations, Dublin, Ireland}
%
%\thanks{{}$^{(7)}$ University of Huddersfield, School of Computing and Engineering, Huddersfield, UK}
%
%\thanks{{}$^{(9)}$ Saarland University, Saarbr\"{u}cken, Germany}
%
%\thanks{{}$^{(10)}$ Department of Astrophysical Sciences, Princeton University, Princeton, NJ, USA}
%
%\thanks{{}$^{(11)}$ University of Illinois, Champaign, IL, USA}

@@

>>>>

\author{Daniel S. Katz$^{(1)}$, Sou-Cheng T. Choi$^{(2)}$, Nancy Wilkins-Diehr$^{(3)}$, Neil Chue Hong$^{(4)}$, 
\\James Howison$^{(5)}$, Miguel de Val-Borro$^{(6)}$, Richard Littauer$^{(7)}$, more TBD %by contributions 
\\{\scriptsize\today \quad  (Due:  $\backsim$ April 30)}} 
%\author{Gabrielle Allen$^{(11)}$,  \\
%Karen Cranston$^{(4)}$, Manish Parashar$^{(5)}$, David Proctor$^{(6)}$, \\
%Matthew Turk$^{(2)}$, Colin C. Venters$^{(7)}$,  Miguel de Val-Borro$^{(10)}$}
%
\thanks{{}$^{(1)}$ Computation Institute, University of Chicago \& Argonne National Laboratory, Chicago, IL, USA}
%
\thanks{{}$^{(2)}$ NORC at the University of Chicago and   Illinois Institute of Technology, Chicago, IL, USA}
%
\thanks{{}$^{(3)}$ University of California-San Diego, San Diego, CA, USA}
%
\thanks{{}$^{(4)}$ Software Sustainability Institute, University of Edinburgh, Edinburgh, UK}
%
\thanks{{}$^{(5)}$ TBD}
%
\thanks{{}$^{(6)}$ TBD}  
%
\thanks{{}$^{(7)}$ TBD}   
%  
%\thanks{{}$^{(4)}$ National Evolutionary Synthesis Center, Durham, NC, USA}
%
%\thanks{{}$^{(5)}$ Rutgers Discovery Informatics Institute, Rutgers University, New Brunswick, NJ, USA}
%
%\thanks{{}$^{(6)}$ International Consortium of Research Staff Associations, Dublin, Ireland}
%
%\thanks{{}$^{(7)}$ University of Huddersfield, School of Computing and Engineering, Huddersfield, UK}
%
%\thanks{{}$^{(9)}$ Saarland University, Saarbr\"{u}cken, Germany}
%
%\thanks{{}$^{(10)}$ Department of Astrophysical Sciences, Princeton University, Princeton, NJ, USA}
%
%\thanks{{}$^{(11)}$ University of Illinois, Champaign, IL, USA}

@@

WSSSPE has developed an engaging online mechanism via the online social network
Twitter (hashtag ``\#WSSSPE''). There were substantially more tweets during
WSSSPE2 than WSSSPE1 or WSSSPE1.1. The WSSSPE community counts 178 tweets and
61 folllowers between May 16, 2013 to April 18, 2015. Some tweets were re-tweeeted or like more than the others.
Table~\ref{tab:tweets} summarizes the top posts and their statistics.

 \begin{table*}[t]
 \centering
\caption{Top tweets of \#WSSSPE.}\label{tab:tweets}
  \begin{scriptsize}
  \begin{tabular}{ l|l|l|r|r}
    Source & Date & Tweet  & Retweets &  Favorites
\\ \hline Software Carpentry & Nov 17 & You call it ``project planning'' if it hasn't started yet,          & 8 & 1
\\                          & &  and``software sustainability'' if it has and wasn't planned.     &    & 
%
\\ Neil P Chue Hong  & Nov 16 &  Here's @SoftwareSaved guidance on Writing and using a software & 7 & 1
\\     & & management plan used by EPSRC software grants    &    &  
\\     & & http://www.software.ac.uk/resources/guides/software-management-plans  &    & 
%
\\ Neil P Chue Hong  & Nov 16 &  @jameshowison as well as software plans   & 4 & 7
\\   & &  http://www.software.ac.uk/resources/guides/software-management-plans &    & 
\\   & &  we provide a software evaluation tool:   &    & 
\\   & &  http://www.software.ac.uk/online-sustainability-evaluation  &    & 
%
\\ Dr Tom Crick & Nov 16 & $56\%$ of UK researchers develop their own software $\rightarrow  140,000$   &  14 & 8
\\ & & UK researchers write research software w$/$out any formal training &    & 
%
\\ Karthik Ram &  Nov 16 &  ``Institutionalize metadata before metadata institutionalizes you'' & 8 & 6
%
\\ Josh Greenberg &  Nov 16 &  ``1. retract any paper with bitrotten dependencies'' *mic drop* & 13 & 8
\\   & &  ``2. add anyone who fixes bitrot as an author'' *mic drop*  &    & 
%
\\ Ethan White &  Nov 16 & ``@rOpenSci is all about community... our measures of success  & 9 & 3
\\ & &  [include] how many faces are up on our community page''   &    & 
%
\\ Ethan White &  Nov 16 & Daniel Katz talking about implementing transitive credit for  & 9 & 7
\\ & & software http://arxiv.org/abs/1407.5117  Work with @arfon  &    & 
% 
\\ Aleksandra Pawlik &  Nov 16 &  ``Tell us how you test your scientific software'' @gvwilson @swcarpentry  & 7 & 2
% 
\\ Aleksandra Pawlik &  Nov 16 & Lack of training as one of the main barriers for sustainable software & 7 & 2
\\ & &   at @Supercomputing. @swcarpentry @datacarpentry can fix that!  & & 
%
\\ Kaitlin Thaney &  Nov 16 & My slides from this morning's keynote at & 11 & 12
\\ & & WSSSPE on Designing for Truth, Scale $+$ Sustainability:  & & 
\\ & &  http://www.slideshare.net/kaythaney/     & & 
\\ & & designing-for-truth-scale-and-sustainability-wssspe2-keynote   & & 
%
\\ Neil P Chue Hong  & Nov 16 & @kaythaney shout out for @swcarpentry @datacarpentry & 9 & 4
\\ & & @rOpenSci @stilettofiend around open training activities for sustainability  & & 
%
\\ Richard Littauer  & Nov 16 &  Sweet! @swcarpentry has had 4000+ learners in the past year. & 6 & 
\\
    \end{tabular}
    \end{scriptsize}
\end{table*}
